Modelling M/EEG data with Bayesian nonparametric multilevel models

### 2025-02-06 brms_meeg.qmd
minor cosmetic updates

Models were fitted using the `brms` package [@burkner_brms_2017; @burkner_advanced_2018; @nalborczyk2019]...

@@

Now, we want to *test* whether the group-level average decoding accuracy is above chance (i.e., 0.5) at each timestep. We use a similar GAM/GP as previously, but we replace the $\mathrm{Normal}$ likelihood function by a $\mathrm{Beta}$ one.

@@

```{r, echo = FALSE}
# citing the R packages we have used
cite_packages(output = "paragraph", omit = NULL, out.dir = ".")
```

>>>>

Models were fitted using the `brms` package [@brms2017; @brms2018; @nalborczyk2019]...

@@

Now, we want to *test* whether the group-level average decoding accuracy is above chance (i.e., 0.5) at each timestep. We use a similar GAM/GP as previously, but we replace the $\mathrm{Normal}$ likelihood function by a $\mathrm{Beta}$ one to account for the bounded nature of AUC values (between 0 and 1).

@@

```{r, echo = FALSE}
# citing the R packages we have used
cite_packages(
    output = "paragraph",
    # omit = c("permuco", "brms", "reticulate"),
    omit = c("permuco", "reticulate"),
    out.dir = "."
    )
```

### 2025-02-06 brms_meeg.tex
minor cosmetic updates

Models were fitted using the \texttt{brms} package
(\citeproc{ref-burkner_brms_2017}{Bürkner, 2017a},
\citeproc{ref-burkner_advanced_2018}{2018a};
\citeproc{ref-nalborczyk2019}{Nalborczyk et al., 2019})\ldots{}

@@

Now, we want to \emph{test} whether the group-level average decoding
accuracy is above chance (i.e., 0.5) at each timestep. We use a similar
GAM/GP as previously, but we replace the \(\mathrm{Normal}\) likelihood
function by a \(\mathrm{Beta}\) one.

@@

We used R version 4.2.3 (\citeproc{ref-base}{R Core Team, 2023}) and the
following R packages: brms v. 2.22.0 (\citeproc{ref-brms2017}{Bürkner,
2017b}, \citeproc{ref-brms2018}{2018b}, \citeproc{ref-brms2021}{2021}),
changepoint v. 2.2.4 (\citeproc{ref-changepoint2022}{Killick et al.,
2022b}; \citeproc{ref-changepoint2014}{Killick \& Eckley, 2014}),
grateful v. 0.2.10 (\citeproc{ref-grateful}{Rodriguez-Sanchez \&
Jackson, 2023}), knitr v. 1.45 (\citeproc{ref-knitr2014}{Xie, 2014},
\citeproc{ref-knitr2015}{2015}, \citeproc{ref-knitr2023}{2023}),
MetBrewer v. 0.2.0 (\citeproc{ref-MetBrewer}{Mills, 2022}), pakret v.
0.2.2 (\citeproc{ref-pakret}{Gallou, 2024}), patchwork v. 1.2.0
(\citeproc{ref-patchwork}{T. L. Pedersen, 2024}), permuco v. 1.1.3
(\citeproc{ref-permuco}{Frossard \& Renaud, 2021b}), rmarkdown v. 2.29
(\citeproc{ref-rmarkdown2024}{Allaire et al., 2024};
\citeproc{ref-rmarkdown2018}{Xie et al., 2018},
\citeproc{ref-rmarkdown2020}{2020}), scales v. 1.3.0
(\citeproc{ref-scales}{Wickham et al., 2023}), scico v. 1.5.0
(\citeproc{ref-scico}{T. L. Pedersen \& Crameri, 2023}), tidybayes v.
3.0.6 (\citeproc{ref-tidybayes}{Kay, 2023}), tidyverse v. 2.0.0
(\citeproc{ref-tidyverse}{Wickham et al., 2019}).

@@

\bibitem[\citeproctext]{ref-burkner_brms_2017}
Bürkner, P.-C. (2017a). \textbf{Brms} : {An} {{\emph{R}}} {Package} for
{Bayesian Multilevel Models Using} {{\emph{Stan}}}. \emph{Journal of
Statistical Software}, \emph{80}(1).
\url{https://doi.org/10.18637/jss.v080.i01}

\bibitem[\citeproctext]{ref-brms2017}
Bürkner, P.-C. (2017b). {brms}: An {R} package for {Bayesian} multilevel
models using {Stan}. \emph{Journal of Statistical Software},
\emph{80}(1), 1--28. \url{https://doi.org/10.18637/jss.v080.i01}

\bibitem[\citeproctext]{ref-burkner_advanced_2018}
Bürkner, P.-C. (2018a). Advanced {Bayesian Multilevel Modeling} with the
{R Package} brms. \emph{The R Journal}, \emph{10}(1), 395.
\url{https://doi.org/10.32614/RJ-2018-017}

\bibitem[\citeproctext]{ref-brms2018}
Bürkner, P.-C. (2018b). Advanced {Bayesian} multilevel modeling with the
{R} package {brms}. \emph{The R Journal}, \emph{10}(1), 395--411.
\url{https://doi.org/10.32614/RJ-2018-017}

>>>>

Models were fitted using the \texttt{brms} package
(\citeproc{ref-brms2017}{Bürkner, 2017}, \citeproc{ref-brms2018}{2018};
\citeproc{ref-nalborczyk2019}{Nalborczyk et al., 2019})\ldots{}

@@

Now, we want to \emph{test} whether the group-level average decoding
accuracy is above chance (i.e., 0.5) at each timestep. We use a similar
GAM/GP as previously, but we replace the \(\mathrm{Normal}\) likelihood
function by a \(\mathrm{Beta}\) one to account for the bounded nature of
AUC values (between 0 and 1).

@@

We used R version 4.2.3 (\citeproc{ref-base}{R Core Team, 2023}) and the
following R packages: brms v. 2.22.0 (\citeproc{ref-brms2017}{Bürkner,
2017}, \citeproc{ref-brms2018}{2018}, \citeproc{ref-brms2021}{2021}),
changepoint v. 2.2.4 (\citeproc{ref-changepoint2022}{Killick et al.,
2022b}; \citeproc{ref-changepoint2014}{Killick \& Eckley, 2014}),
grateful v. 0.2.10 (\citeproc{ref-grateful}{Rodriguez-Sanchez \&
Jackson, 2023}), knitr v. 1.45 (\citeproc{ref-knitr2014}{Xie, 2014},
\citeproc{ref-knitr2015}{2015}, \citeproc{ref-knitr2023}{2023}),
MetBrewer v. 0.2.0 (\citeproc{ref-MetBrewer}{Mills, 2022}), pakret v.
0.2.2 (\citeproc{ref-pakret}{Gallou, 2024}), patchwork v. 1.2.0
(\citeproc{ref-patchwork}{T. L. Pedersen, 2024}), rmarkdown v. 2.29
(\citeproc{ref-rmarkdown2024}{Allaire et al., 2024};
\citeproc{ref-rmarkdown2018}{Xie et al., 2018},
\citeproc{ref-rmarkdown2020}{2020}), scales v. 1.3.0
(\citeproc{ref-scales}{Wickham et al., 2023}), scico v. 1.5.0
(\citeproc{ref-scico}{T. L. Pedersen \& Crameri, 2023}), tidybayes v.
3.0.6 (\citeproc{ref-tidybayes}{Kay, 2023}), tidyverse v. 2.0.0
(\citeproc{ref-tidyverse}{Wickham et al., 2019}).

@@

\bibitem[\citeproctext]{ref-brms2017}
Bürkner, P.-C. (2017). {brms}: An {R} package for {Bayesian} multilevel
models using {Stan}. \emph{Journal of Statistical Software},
\emph{80}(1), 1--28. \url{https://doi.org/10.18637/jss.v080.i01}

\bibitem[\citeproctext]{ref-brms2018}
Bürkner, P.-C. (2018). Advanced {Bayesian} multilevel modeling with the
{R} package {brms}. \emph{The R Journal}, \emph{10}(1), 395--411.
\url{https://doi.org/10.32614/RJ-2018-017}
